Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Next, we aim to produce, for each pair $(h, r) \in H \times r$ such that $r$ crosses $h$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.

@@

Each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a containment query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. The sum $\sum_h K_h$ here is equal to the total size of $\contained_R(h)$ for all the $h \in H$. The total size is equivalent to $\out$. The cost so far is therefore $O(n \log n + \out)$.

>>>>

Next, we aim to produce, for each pair $(h, r) \in H \times r$ such that $h$ crosses $r$, a pair $(h, \lambda)$ where $\lambda$ is the ID of $r$. These pairs may be output in an arbitrary order. Sort the set of y-coordinates defined by all the horizontal segments and rectangles. Sweep (conceptually) a horizontal line $\ell$ from $y = -\infty$ to $y = \infty$. At all times, we maintain the set $R_\ell$ of rectangles in $R$ that intersect with $\ell$. Let $S_\ell$ be the set of x-ranges of the rectangles in $R_\ell$; we store $S_\ell$ in a PST $\T$. Specifically, when $\ell$ hits the bottom (resp., top) edge of a rectangle $r = [x_1, x_2] \times [y_1, y_2]$ of $R$, we insert (resp., delete) $[x_1, x_2]$ into (resp., from) $\T$, which can be done in $O(\log n)$ time. We call the rectangle $r$ the {\em host} of $[x_1, x_2]$ and store its ID together with $[x_1, x_2]$ in $\T$. When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a reverse-containment query on $\T$ to find all the intervals in $S_\ell$ that contain $[z_1, z_2]$; the query cost is $O(\log n + K_h)$, where $K_h$ is the number of intervals reported. For each retrieved interval $[x_1, x_2]$, we also obtain the ID $\lambda$ of its host rectangle $r$, and output the pair $(h, \lambda)$.

@@

Each rectangle of $R$ necessitates one insertion and one deletion in $\T$. All these insertions and deletions take $O(n \log n)$ time in total. Each segment $h$ of $H$ performs a reverse-containment query on $\T$, which has a cost of $O(\log n + K_h)$. All these queries demand a total cost of $O(n \log n + \sum_h K_h)$. The sum $\sum_h K_h$ here is equal to the total size of $\contained_R(h)$ for all the $h \in H$. The total size is equivalent to $\out$. The cost so far is therefore $O(n \log n + \out)$.
